### 2020-07-13 nb/analysis_in_R.Rmd
define MarkovExpectedGoals

@@

    home_score <- matrix(0, nrow=20, ncol=20)
    colnames(home_score) <- teams
    rownames(home_score) <- teams

@@

    league_table <- matrix(0, nrow=20, ncol=8)
    rownames(league_table) <- teams
    colnames(league_table) <- c('POS','PTS','W','D','L','GF','GA','GD')

@@

        for (team in c(home_team, away_team)){
            league_table[team,'GD'] <- league_table[team,'GF'] - league_table[team,'GA']
            league_table[team,'PTS'] <- 3*league_table[team,'W'] + 1*league_table[team,'D']
        }

    }
    return(list(league_table, home_score, away_score))
}
```

```{r}
results <- LeagueResults(events)
```

```{r}
league_table <- data.frame(results[[1]])
```

```{r}
league_table[order(-league_table$PTS),]
```

@@

@@

```{r}
match_id <- '2500032'
```

@@

```{r}
PassNetwork(events, match_id, team_colour='blue')
PassNetwork(events, match_id, home_or_away='Away', flip=T)
```

@@

    game <- events[events$matchId == match_id,]
    game <- game[game$source!='' & game$target!='nan',]

@@

@@

```{r}
x_score_time <- ExpectedScoringTime(
    TransitionMatrix(
        GameGraph(events, match_id, home_or_away='Home'))

```{r}
x_score_time/mean(x_score_time)
```

```{r}
x_score_time/mean(x_score_time)
```

```{r}
names(transition_matrix[1,])[1:(nrow(transition_matrix)-2)]
```

```{r}
max_steps <- 10000
transition_matrix <- TransitionMatrix(GameGraph(events, match_id))
state_probabilities <- matrix(NA,nrow=max_steps+1,ncol=ncol(transition_matrix),dimnames=list(0:max_steps,(ncol(transition_matrix)-1):0))
vector <- rep(0,ncol(transition_matrix))
vector[6] <- 1
state_probabilities[1,] <- vector

probs <- diff(state_probabilities[,ncol(transition_matrix)])
sum(probs*seq_along(probs))
```

```{r}
transition_matrix
```

>>>>

```{r}
events[1:10,]
```

@@

    home_score <- matrix(0, nrow=length(teams), ncol=length(teams))
    colnames(home_score) <- teams
    rownames(home_score) <- teams

@@

    league_table <- matrix(0, nrow=length(teams), ncol=9)
    rownames(league_table) <- teams
    colnames(league_table) <- c('Pos','Pld','W','D','L','GF','GA','GD','Pts')

@@

        for (team in c(home_team, away_team)){
            league_table[team,'GD'] <- league_table[team,'GF'] - league_table[team,'GA']
            league_table[team,'Pts'] <- 3*league_table[team,'W'] + 1*league_table[team,'D']
            league_table[team,'Pld'] <- league_table[team,'Pld'] + 1
        }

    }

    league_table <- league_table[order(-league_table[,'Pts']),]

    league_table[,'Pos'] <- 1:20

    return(league_table)
}
```

```{r}
prem <- LeagueResults(events)
```

```{r}
pl <- as.data.frame(prem)
```

```{r}
pl['Team'] <- rownames(pl)
```

```{r}
pl2 <- as.data.frame(pl[,c(10,2:9)])
```

```{r}
rownames(pl2) <- c()
```

```{r}
pl2[1:5,]
```

```{r}
prem[1:5,]
```

```{r}
NationalResults <- function(nation) {

    data <- LoadAndScaleData(nation)
    results <- LeagueResults(data)
    return(results)
}

@@

```{r}
correct_res <- read.csv('../data/league_results/England17-18.csv')
```

```{r}
correct_res
```

```{r}
france <- NationalResults('France')
germany <- NationalResults('Germany')
italy <- NationalResults('Italy')
spain <- NationalResults('Spain')
```

```{r}
premiership <- NationalResults('England')
```

@@

```{r}
#away vs Crystal Palace
match_id <- '2500032'
```

```{r}
# vs man city
match_id <- '2499943'
```

@@

```{r}
PassNetwork(events, match_id, team_colour='red')
PassNetwork(events, match_id, team_colour='blue', home_or_away='Away', flip=T)
```

```{r}
2499943
```

@@

    game <- events[events$matchId == match_id,]
    game <- game[game$source!='' & game$target!='' & game$target!='nan',]

@@

    team_graph$team <- team_name
    team_graph$opposition <- opposition_team
    team_graph$status <- home_or_away

@@

```{r}
SeasonAdjacencyMatrix <- function(events, team) {

    players <- unique(events[events$team==team & events$source!='' & events$target!='',]$source)
    n <- length(players) + 2
    squad_adj <- matrix(0,nrow=n,ncol=n)
    rownames(squad_adj) <- c(as.character(players), 'Opposition', 'Goal')
    colnames(squad_adj) <- rownames(squad_adj)

    games <- unique(events[events$team==team,]$matchId)

    for (game in games){

        # get graph and adjacency matrix for game
        game_graph <- GameGraph(events, game, team)
        game_adj <- AdjacencyMatrix(game_graph)

        # add values of game adjacency matrix to full-season matrix
        for (source in rownames(game_adj)){
            for (target in colnames(game_adj)){
                squad_adj[source,target] <- squad_adj[source,target] + game_adj[source,target]
            }
        }
    }

    return(squad_adj)
}
```

```{r}
MarkovExpectedGoals <- function(events, season_adjacency_matrix) {

    season_graph <- graph_from_adjacency_matrix(season_adjacency_matrix)
    season_transition <- TransitionMatrix(season_graph)
    seasonXST <- ExpectedScoringTime(season_transition)
    avg_events_per_game <- nrow(events)/380
    mXG <- sort(avg_events_per_game/seasonXST, decreasing=T)

    return(mXG)
}
```

```{r}
GoalProbabilities <- function(season_adjacency_matrix) {

    season_graph <- graph_from_adjacency_matrix(season_adjacency_matrix)
    season_transition <- TransitionMatrix(season_graph)
    goal_probs <- sort(season_transition[,'Goal'],T)[2:nrow(season_transition)] * 100

    return(goal_probs)
}
```

```{r}
liverpool_adj <- SeasonAdjacencyMatrix(events,'Liverpool')

```{r}
mXG <- MarkovExpectedGoals(events, liverpool_adj)
```

```{r}
mXG
```

```{r}
GoalProbabilities(liverpool_adj)
```

```{r}
sort(liverpool_adj[,'Goal'],T)
```

```{r}
g <- GameGraph(events, match_id, home_or_away='Home')
```
